%!TEX TS-program = xelatex
\documentclass[a4paper]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{roderik}{koenders}
       {data scientist}

\hypersetup{
    pdftitle={Roderik Koenders - CV - Data Scientist},
    pdfauthor={Roderik Koenders},
    pdfkeywords={resume, CV, data scientist, remote sensing, planetary science},
}

% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    Soestdijksekade 1124
    2574 EP `s Gravenhage
    The Netherlands
    ~
    %\href{mailto:roderikk@gmail.com}{roderikk@gmail.com}
    %\href{http://roderikk.nl}{http://roderikk.nl}
    roderikk@gmail.com
    http://roderikk.nl
    +31 6 10 38 38 08
    ~
    %\href{http://facebook.com/adrien}{fb://adrien}
  \section{languages}
    bilingual dutch/english
    italian
  \section{programming}
    %{\color{red} $\varheartsuit$} 
    Python
    Java, Mathematica
    QGis
    SQL
    CCS \& HTML
  \section{hobbies}
    photography
    travel
    (water) sports
    table-top gaming
\end{aside}

%\vspace{2.5\parskip}
\section{about}

% As a researcher I have become adept at looking at a problem from multiple angles.
% The fields of study I have chosen have allowed me to cooperate with people from many disciplines, (aero)space engineers, geologists, data analysts and remote sensing experts.
% This has taught me to always look for cross-domain applications.
% The international work environments and collaborations I have pursued have made me into a team player.

I am looking for a work environment that provides challenges in the form of dedicated problems.
An environment where I can apply myself individually, and as an integral part of a team.
And an environment that gives me the space to develop my own ideas and search for synergies with other aspects of the business.

%\section{keywords}

\textbf{Keywords} : 
\emph{data mining},
\emph{remote sensing},
\emph{image processing},
\emph{planetary science},
\emph{passionate},
\emph{always looking for new challenges},
\emph{cross-domain applications},
\emph{motivator},
\emph{team player}

\section{education}

\begin{entrylist}
  \entry
    {since 2009}
    {Ph.D. {\normalfont candidate in Remote Sensing}}
    {Delft University of Technology}
    {\emph{A multiscale approach for extracting channels from digital elevation methods.}}
  \entry
    {2005-2009}
    {M.Sc. summa cum laude}
    {Delft University of Technology}
    {Majoring in Aerospace Engineering\\
    Optimization of Landing-Site Selection for ExoMars.}
  \entry
    {2002–2005}
    {B.Sc.}
    {Delft University of Technology}
    {Majoring in Aerospace Engineering}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {since 2009}
    {Researcher}
    {Delft University of Technology}
    { {\addfontfeature{Color=lightgray}Skills:} {image processing, data analysis, fieldwork, geology, grant and article writing, teaching, supervision, determination} \\
      {\addfontfeature{Color=lightgray}Role:} {Research as part of my doctoral thesis. I have worked on several research projects with tight deadlines. I have applied for my own funding streams. Educational activities with B.Sc. and M.Sc. students. Cross-domain collaboration with geologists. Geological fieldwork in Morocco, France. }}
  \entry
    {2012–2013}
    {Co-founder}
    {Ortsa Prime}
    { {\addfontfeature{Color=lightgray}Skills:} { business, finance, managing a group } \\
    {\addfontfeature{Color=lightgray}Role:} {Business initiation phase for a software start-up. }}
  \entry
    {2009–2011}
    {Researcher, developer}
    {Utrecht University}
    { {\addfontfeature{Color=lightgray}Skills:} { building a web platform, organization of a large event } \\
    {\addfontfeature{Color=lightgray}Role:} {Contract for EuroPlanet to create a website to foster the international planetary society, PlanetaryGIS.org. 
    Organization of the International Workshop on Landing Site Selection in Leiden.}}
  \entry
    {2007–2009}
    {Software Developer}
    {S[\&]T}
    { {\addfontfeature{Color=lightgray}Skills:} { programming, software engineering, working with a deadline } \\
    {\addfontfeature{Color=lightgray}Role:} { Developer for the \href{http://crewassistant.com}{MECA} project. 
            Development of various systems at NATO, subcontracted from S\&T. 
            Design and development of the hour administration tool of S\&T in Django. 
            Design and development of the S\&T website.}}
  \entry
    {2007–2008}
    {Research Internship}
    {ESA/ESTEC}
    { {\addfontfeature{Color=lightgray}Skills:} { research, networking, working in an international environment } \\
    {\addfontfeature{Color=lightgray}Role:} {Optimizing landing-site selection for ExoMars: Developing a decision support system for landing-site selection. }}
  % \entry
  %   {01–07 2007}
  %   {\href{http://stcorp.nl}{S\&T}}
  %   {Internship}
  %   {\emph{Developer for the \href{http://crewassistant.com}{MECA} project. }}
  \entry
    {2004}
    {Data analyst}
    {Regional Amsterdam Police Force (RPAA)}
    { {\addfontfeature{Color=lightgray}Skills:} { office work, data analysis } \\
    {\addfontfeature{Color=lightgray}Role:} {Analyzing data to provide management with up-to-date statistical information. }}
  \entry
    {2004–2007}
    {Sports Instructor}
    {Kanoschool.nl}
    { {\addfontfeature{Color=lightgray}Skills:} { event organization, managing large groups, safety } \\
    {\addfontfeature{Color=lightgray}Role:} {Waveski and Raft instructor for large groups along the Dutch coastline. }}
  % \entry
  %   {05–10 2001}
  %   {Regional Amsterdam Police Force (RPAA)}
  %   {Developer}
  %   {\emph{Development and design of an online Crisis Manual for the department of Crisis Management. }}
\end{entrylist}

\section{achievements}

\begin{entrylist}
  \entry
    {2009}
    {Best Graduate Award}
    {Delft University of Technology}
    {Awarded best graduate of the year 2009 for the faculty of Aerospace Engineering.}
  \entry
    {2006, 2008}
    {Team Leader}
    {Dutch National Kayak Team}
    {Team leader for European Championships Under 23 Kayaking in Athens, Greece and Szeged, Hungary.}
  \entry
    {2008}
    {PlanetaryGIS.org}
    {PlanetaryGIS.org}
    {Community based website to collaborate on planetary science by planetary scientists.}
  \entry
    {2004}
    {Championships}
    {Kayaking Championships}
    {Finished tenth place on K1 200 meters in European Championships Kayaking. \\
    Semi-final on K2 500 and 1000 meters in European Championships Under 23 Kayaking. \\
    Dutch National Champion Kayaking on K1 200 meters, and K2 200, 500, and 1000 meters.
    }
\end{entrylist}

\section{publications}

\printbibsection{article}{article in peer-reviewed journal}
\begin{refsection}
  \nocite{*}
  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
\end{refsection}
\begin{refsection}
  \nocite{*}
  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
